---
output: github_document
---

# Welcome to the transportDataManchester repo

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This is a package to ease the access and analysis of open transport data in Manchester. It comes pre-installed with some datasets and automatically installs some useful software for visualising spatial data on your computer.

## Pre-requisites

Recent versions of R (which can be downloaded [here](https://www.r-project.org/)) and [RStudio](https://www.rstudio.com/products/rstudio/download/).

This is free software that works on Linux, Mac and Windows.

It is suggested you get up-to-speed with RStudio, for example with reference to this tutorial: https://github.com/Robinlovelace/Creating-maps-in-R (Lovelace et al. 2014)

## Installation

Open RStudio and enter the following, to install the 'devtools' package:

```{r, eval=FALSE}
install.packages("devtools")
```

Then you can install this package:

```{r, eval=FALSE}
devtools::install_github("robinlovelace/transportDataManchester")
```

Load it as follows:

```{r}
library(transportDataManchester)
```


## Using the package

The package comes with a number of datasets pre-installed. To see them try:

```{r, eval=FALSE}
data(package = "transportDataManchester")
```

To plot the cycle path data, for example, try the following:

```{r cycle_route_map}
library("tmap") # load mapping package
data("cycle_routes")
osm_tiles = read_osm(bb(cycle_routes))
cycle_routes$`Year opened` = as.character(cycle_routes$OpeningYea)
qtm(osm_tiles) +
  tm_shape(cycle_routes) +
  tm_lines(col = "Year opened", palette = "Spectral")
```

## Further data resources

There are many open data resources available, in addition to the `cycle_routes` dataset included in the package:

## Cycle data

- Data from the Propensity to Cycle Tool: http://www.pct.bike/

- Cycle routes (this is where the `cycle_routes` dataset pre-installed in this package is from): https://data.gov.uk/dataset/gm-cycle-routes

- Cycle hubs: https://data.gov.uk/dataset/gm-cycle-hubs

- Cycle lockers: https://data.gov.uk/dataset/gm-cycle-lockers

- Cycle parking: https://data.gov.uk/dataset/gm-cycle-parking

- Bike shops: https://data.gov.uk/dataset/cycle-shops

### Other TfGM data

- GM Traffic Signal Locations : https://data.gov.uk/dataset/traffic-signal-locations

- Greater Manchester Road Casualty Statistics: https://data.gov.uk/dataset/greater-manchester-road-casualty-statistics

- Metrolink Stops and Rail Stations: https://data.gov.uk/dataset/metrolink-and-rail-stations

- GM Public Transport Schedule – GTFS: https://data.gov.uk/dataset/public-transport-schedules-gtfs

- Car Parks - http://developer.tfgm.com/ (requires registration) (also, note that this will be replaced by a new live system soon but the concept will be the same so can be used on a Proof of Concept basis)

### External data - Air Quality

- Air Quality Management Areas - https://uk-air.defra.gov.uk/aqma/maps

- Great Air Manchester - http://www.greatairmanchester.org.uk/GreatAir/default.aspx

- Air Quality England - http://www.airqualityengland.co.uk/

## References

Lovelace, R., & Cheshire, J. (2014). Introduction to visualising spatial data in R.
