---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This is a package to ease the access and analysis of open transport data in Manchester. It comes pre-installed with some datasets and automatically installs some useful software for visualising spatial data on your computer.

## Pre-requisites

Recent versions of R (which can be downloaded [here](https://www.r-project.org/)) and [RStudio](https://www.rstudio.com/products/rstudio/download/).

This is free software that works on Linux, Mac and Windows.

It is suggested you get up-to-speed with RStudio, for example with reference to this tutorial: https://github.com/Robinlovelace/Creating-maps-in-R (Lovelace et al. 2014)

## Installation

Open RStudio and enter the following, to install the 'devtools' package:

```{r, eval=FALSE}
install.packages("devtools")
```

Then you can install this package:

```{r, eval=FALSE}
devtools::install_github("robinlovelace/transportDataManchester")
```

## Using the package



## References

Lovelace, R., & Cheshire, J. (2014). Introduction to visualising spatial data in R.
